---
title             : "A collaborative review of issues in Instance Memory"
shorttitle        : "Instance Memory"

author: 
  - name          : "Matthew J. C. Crump"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "2900 Bedford Avenue, Brooklyn, 11210"
    email         : "mcrump@brooklyn.cuny.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "TBD"
    affiliation   : "1"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Brooklyn College of CUNY"
  - id            : "2"
    institution   : "Graduate Center of CUNY"

authornote: |
  Correspondence concerning this article should be addressed to Matthew J. C. Crump, Department of Psychology, Brooklyn College of the City University of New York, 2900 Bedford Avenue, Brooklyn, NY 11210.

abstract: |
  This abstract needs to be completed.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["InstanceMemory.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "jou"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

## Introduction

<!-- this is a comment -->

The purpose of this document is to review issues related to instance-based perspectives on cognition. The intention is that this document will be created collaboratively by members of the Computational Cognition Laboratory at Brooklyn College of the City University of New York.

Topics for review include classic perspectives, theories, and models of instance-based processes in cognition; and, debates between instance-based perspectives and other cognitive theories as they relate to explanations of cognitive phenomena. It is also worth focusing on linkages between predictions of instance theory and evidence of those predictions in the empirical records. In other words, what manipulations, measures, and domains are commonly used to supply evidence for instance-based processing.

As this review document grows it should supply new students with a repository of knowledge about instance-based processing that they can use to guide their scholarship in this domain. Contributions to this review should also focus on identifying new topics for study that relate or extend prior topics.





\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
